---
title: "Covid_19 Animated plot on death cases"
author: "Vishnu Prasad  J S"
date: "2/8/2021"
output: html_document
---
The library that are used for this code are `tidyverse` and `gganimate`   
*steps*     
1. Initial data set is loaded into the variable `Data` as csv file    
2. Data is then grouped by date.  
3. New variable rank is introduced using the `mutate()` function and the countries are ranked according to the death count.  
4. Again on the grouped by date data, a new grouping of country is applied.  
5. Finally the top 10 countries on each day are filtered.by using countries having rank `< 15`
 then the data is grouped by country name   
 
```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(gganimate)
Data <-read.csv ("full_grouped.csv", header =T) 
death10 <- Data %>%
  group_by(Date) %>%
  mutate(rank = rank(-Deaths),
         Value_lbl = paste0(" ",Deaths)) %>%
  group_by(Country.Region) %>% 
  filter(rank <=15) %>%
  ungroup()


```
A static plot is generated for a particular year and with the additional formatting done so as to make the plot look good.

```{r message=FALSE, warning=FALSE}
staticplot = ggplot(death10, aes(rank, group = Country.Region, 
                                      fill = as.factor(Country.Region), color = as.factor(Country.Region))) +
  geom_tile(aes(y = Deaths/2,height = Deaths,width = 0.9), alpha = 0.8, color = NA) +
  geom_text(size=8,aes(y = 0, label = paste(Country.Region, " ")), vjust = 0.2, hjust = 1) +
  geom_text(size=8,aes(y=Deaths,label = Value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=27, hjust=0.5, face="bold", colour="black", vjust=-1),
        plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
        plot.margin = margin(2,4, 2, 12, "cm"))

```

Finally the static plot is called over all the years to get an animated plot of the covid death reported in each country over the dates.

```{r message=FALSE, warning=FALSE}

anim = staticplot + transition_states(Date, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  +
  labs(title = 'Covid-19 Total Death Cases : {closest_state}',  
       subtitle  =  "Top 10 Countries",
       caption  = "Death Cases | Data Source: WHO ")
animate(anim, 1000, fps = 30,  width = 1200, height = 1000, 
        renderer = gifski_renderer("Covid_deaths.gif"))
```